Implementation Design Patters for Pursuit-Evasion Problems with Bounded Speed

### 2012-12-01 paper.tex
added some diagrams
completed diagrams

@@

@@

%sexy diagram

@@

@@

An issue that may arise is evader travel time in a triangle/vertex may be less than the estimated contamination delay. An evader may only spend a moment crossing a corner of a triangle and jump ahead of the spreading contamination, for example. To help alleviate this error ahead of time, one can subdivide a triangle/vertex into three at it's barycentric center. This technique divides areas into smaller regions with faster contamination speeds, allowing for a granularity closer to \(\mathbb{R}^2\).

@@

\section{References}

>>>>

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{"visPoly"}
\caption{A pursuer P in an example R. The visibility polygon for P is shaded in showing the area P can view. Note the edge gaps that bound the visibility polygon and the rest of R. If P were to move as far to the right as possible, the visible area near to the top of R would vanish.}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{"trangulation"}
\caption{A diagram showing the process for deriving \(G\) from \(R\). In (1) the initial environment is visible. Subsequently it is triangulated using Delaunay Triangulation in (2). Finally, adjacent triangles are used to construct the edges and nodes for \(G\) in (3).}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{"visibility"}
\caption{A diagram showing \(R\) divided into triangles according to \(G\) and the visibility according to various pursuer locations. Note that visibility is not a function of which triangle/vertex in \(G\) the pursuer is located in.}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{"contamination"}
\caption{A diagram showing \(R\) with a contamination spreading from the right. Note that the contamination does not necessarily spread at the closest path in the euclidean plane and would require smaller triangles.}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{"tesslation"}
\caption{A diagram showing \(R\) with its triangles subdivided into smaller triangles. Note the population of \(G\) has multiplied by 3. If this were to be continued the triangles would likely be indistinguishable from \(\mathbb{R}^2\).}
\end{figure}

An issue that may arise is evader travel time in a triangle/vertex may be less than the estimated contamination delay. An evader may only spend a moment crossing a corner of a triangle and jump ahead of the spreading contamination, for example. To help alleviate this error ahead of time, one can subdivide a triangle/vertex into three at it's barycentric center. This technique divides areas into smaller regions with faster contamination speeds, allowing for a granularity closer to \(\mathbb{R}^2\). It's important to keep note that \(G\) still keeps its planar status even when subdivided.

@@
